\chapter{Introduction}\label{C:intro}

Historically power distribution has been primarily in the form of AC (Alternating current). This is credited to the fact that AC power is more efficient to transmit over long distances and made it easy to step up and down the voltages efficiently with transformers \cite{Earley2013}. However, with the invention of solid-state electronics such as the metal–oxide–semiconductor field-effect transistor or MOSFET for short, it has become possible to efficiently step up and step down direct current (DC) voltages. This has been achieved by the invention of the switch-mode power supply, which has facilitated the continued reduction of size and increase in efficiency of electronics \cite{Bocock}.

Today, switch-mode power supplies can be found in a wide variety of consumer and professional electronics, with some examples being laptops, phones, and any form of DC charger. Their widespread usage when compared to other DC-DC converters such as linear regulators can be attributed to their far greater efficiency. One such switch-mode power supply is the buck converter, which will step down a DC input voltage to a lower DC output voltage.

\section{Project Motivation}

Although buck converters are a widespread technology, they are not without their limitations and drawbacks. The current buck converter design process requires that a specific output filter be designed around the switching frequency of the converter, and the desired inductor ripple current. This filter design process will often result in the converter requiring discrete passive components that are non-standard and hard to source. This will usually result in the designer having to make compromises in their design for either the cost or the performance of the converter.

Another drawback of this design process is the static nature of both the filter and the switching components once they have been selected. This results in the buck converters desired inductor current ripple only being achieved at a very specific designed output voltage or load. This means that with current buck converter designs varying the desired output voltage or varying the output load will cause the inductor current ripple to vary. This is an issue, as very few loads are static and will not change during their operation. 

\section{Project Goals}\label{S:goals}

The goal of this project is to develop a testing platform through which the effects of variable buck converter switching frequency on inductor current ripple can be observed and controlled. The aim of this is to eliminate the need to design the output stage of the buck converter by implementing a control system to maintain a specified inductor current ripple, and output voltage.\\

To achieve this goal, a proof of concept buck converter will be designed to operate as the testing platform. This converter will require a variable frequency pulse width modulated (PWM) signal generator, and inductor current ripple sensing. This will allow for direct manipulation and control of inductor current ripple. The converter will also need to implement the full functionality of existing buck converter designs, including controlled output voltage regulation.

It is also important to note that as this project aims to produce a testing platform to be used as a proof of concept, there will be continued work undertaken after the projects conclusion. Because of this, it is important that the design and implementation undertaken in this project considers the ease of use and future expansion of the project.\\

The following list of specifications outlines the requirements the designed test platform will meet:

\begin{enumerate}
    \item Operate with a 12V DC input supply voltage
    \item Provide a selectable DC output voltage between 3V and 10V
    \item Provide an output voltage precision of at least $\pm5\%$ of the targeted output voltage
    \item Provide a selectable inductor current ripple between 20\% and 50\% of the total output current
    \item Provide a variable converter switching frequency between 1$k$Hz and 100$k$Hz
    \item Provide an inductor current ripple precision of at least $\pm5$\% of the target inductor current ripple 
    \item Operate with variable load sizes between 10$\Omega$ and 20 $\Omega$
\end{enumerate}


% This project aims to eliminate the need to design the output stage of a buck converter. By implementing a control system that varies the switching frequency of the converter, we will be able to directly manipulate the inductor current ripple. This project aims to produce a proof of concept buck converter that is capable of operating at 12V, with an output range of 3-10V and precision of $\pm5\%$. The converter will also be able vary its switching frequency between 1$kHz$ and 100$kHz$, allowing for selection of inductor current ripple between 20\% and 50\% with precision of $\pm5\%$. All of this must be implemented while maintaining the standard functionality of the converter.


% \subsubsection{TODO Expand on the project goals, possibly convert the previous section into a bulleted list of project goals and requirements.}

% This will be referenced in the implementation and design sections many times, so it needs to clearly outline what we are looking to achieve in this project. 