\chapter{Background}\label{C:background}

A Literature research was performed to inform design decision made in this project, and to evaluate any existing research. It will discuss buck converter design factors and topologies, as well as the various different methods of PWM generation. In performing this literature research, the following terms were used to search for articles from Google Scholar, Engineering Village, and Te Waharoa:

\begin{itemize}
    \item Frequency Variable PWM
    \item Frequency-PWM converter
    \item Switching Frequency Converter
\end{itemize}

These searches returned no research relevant to the designs of this project, with the only related work focusing on the electromagnetic noise reduction using randomised frequency modulation \cite{Roman2001,Familiant2016}. Because of this, research was instead performed to inform the design of the buck converter and the generation of PWM signals.


\section{Buck Converters}

\begin{itemize}

    \item 
    Talk about the use and purpose of buck converters, as well as their basic design factors.

    \item 
    Talk about the different buck converter topologies, and why it is that we have chosen to implement this design on a non-synchronous converter. 

    \item 
    Talk about the buck converter design equations, and specify which equations are relevant to my design.

\end{itemize}



\section{PWM Generation}

\begin{itemize}

    \item 
    Discuss what PWM is, and how it is used in the context of a buck converter.
    
    \item 
    Discuss the different methods of PWM generation. 

    \begin{itemize}
        \item Analogue 
        \item Digital (Microcontroller \& FPGA)
    \end{itemize}

    \item 
    Discuss how PWM is used in the context of the project. Quickly overview how in this project it will be important to modulate both the PWM frequency, and the PWM duty cycle.

\end{itemize}

\section{Control Systems}

Possibly not needed in this report as I have not designed any control systems yet for this project?

\begin{itemize}
    
    \item
    Discuss in very general terms what a control system is what what it seeks to do in a system.

    \item 
    Discuss what the control system will be doing in the case of this project. Talk about how a controller will be used to control both the output voltage of the converter, and the inductor ripple of the converter.  

    \end{itemize}