\chapter{Future Plan}\label{C:future} 

\section{Work to be Completed}

\begin{itemize}

    \item 
    Discuss what work I still have to do before beginning the evaluation of the system. 

    \begin{itemize}
        \item Select sensors to measure peak-to-peak ripple current
        \item finalise the circuit design for the project, this includes selection all other components needed for it's operation.
        \item Create a final PCB for the design 
        \item Design the controller that will control both output voltage and inductor ripple 
    \end{itemize}

\end{itemize}

\section{System Evaluation}


    The evaluation of this project will be based upon meeting the following selection of specifications. All evaluations of the design will be conducted using a 10$\Omega$ output load, with an input voltage of 12V DC.

\begin{itemize}
	\item The buck converter will be able to take input voltages up to 12V DC
	
	\item The buck converter maintains basic functionality of $V_{out} = D\times V_{in} - \mathrm{effeciency}$

	\item The buck converter will output voltages between 3V and 10V DC
	
	\item The output voltage accuracy will be within $\pm 5\%$ of the target output voltage

	\item The user will be able to define the inductor ripple between 20\% and 50\%, with increments of 5\%.
	
	\item The inductor ripple accuracy will be within $\pm 5\%$ of the defined inductor ripple
	
	\item The buck converter will have a switching frequency range of 1k$Hz$ to 100k$Hz$

\end{itemize}

\section{Project Timeline}

\begin{itemize}

    \item 
    Create another Gant chart that now more accurately breaks down the required tasks into the remaining time. Discuss this chart and why it is set out the way that it is. 

\end{itemize}



\section*{Feedback}\label{S:feedback} 

% This could highlight any difficulties currently faced, and make specific requests for guidance from the examination committee. For example, a student may be unsure how best to evaluate their artefact, and would appreciate suggestions for alternative methods. 

\begin{itemize}
    \item I want to ask for some suggestion on evaluating the final artefact. The evaluation described within my proposal has not changed, and it seems to be very simple at the moment.   
\end{itemize}